Our Title

### 2015-05-04 draft.tex
Added in Scott's pre-det nuclear forensics background section.

ISIL poses a more direct threat to its neighbors than to the U.S. homeland. While many foreigners with Western passports have pledged allegiance to ISIL, they often do so with no intent to return, as illustrated by the common burning of passports once individuals reach ISIL territory. Additionally, ISIL must continue to expand, taking territory from “illegitimate” governments, in order to maintain its own legitimacy as a Caliphate.

@@

\subsection{??????? Isotope and nuclear structure section  ????}

@@

The basic process of detonation is as follows: The primary device triggers first and supplies x-rays, which heat the secondary device, which heats the polystyrene foam into a plasma. The Plutonium “spark plug” at the center of the fusion assembly begins to undergo fission due to the compression from the polystyrene plasma. The Lithium-6 deuteride blanket, which surrounds the plutonium spark plug, produces tritium and begins the fusion stage. The flux of neutrons from the fusion reactions causes the \ce{^{238}U} tamper to undergo fission. At this stage the device breaks apart and a detonation is complete \cite{Defense1998}.

@@

>>>>

ISIL poses a more direct threat to its neighbors than to the U.S. homeland. While many foreigners with Western passports have pledged allegiance to ISIL, they often do so with no intent to return, as illustrated by the common burning of passports once individuals reach ISIL territory. Additionally, ISIL must continue to expand, taking territory from \enquote{illegitimate} governments, in order to maintain its own legitimacy as a Caliphate.

@@

\subsection{Nuclear Structure}

Atoms are essentially a dense core of protons and neutrons surrounded by an electron cloud. The neutrons and protons in the nucleus (atomic core) are also known as nucleons, collectively \cite{krane1987introductory}. For the purposes of this report, a complete understanding of the atomic structure is not necessary. However, what should be understood is the difference between an element and an isotope, and how to determine what element and isotope an atom is based on its nuclear composition.

Within the nucleus, the number of protons defines what element an atom is. For example, an atom with six protons is a carbon atom, and an atom with ninety two protons is a uranium atom. The number of total nucleons, or the number of protons and neutrons combined, defines the isotope of the element that the atom is \cite{krane1987introductory}. For example, a carbon atom with six neutrons has twelve nucleons, and is known as a \ce{^{12}C} atom. A uranium atom with one hundred and forty three neutrons has two hundred and thirty five nucleons, and is known as \ce{^{235}U}, an important element in nuclear science and for many nuclear weapons. It is interesting to note that different isotopes of the same element can behave significantly differently. An excellent example of this is that \ce{^{235}U} readily fissions in nuclear reactors and weapons, but \ce{^{238}U} only reliably fissions under specific conditions, and therefore is not a useful fuel in nuclear weapons \cite{krane1987introductory,Duderstadt1976}.

@@

The basic process of detonation is as follows: The primary device triggers first and supplies x-rays, which heat the secondary device, which heats the polystyrene foam into a plasma. The Plutonium \enquote{spark plug} at the center of the fusion assembly begins to undergo fission due to the compression from the polystyrene plasma. The Lithium-6 deuteride blanket, which surrounds the plutonium spark plug, produces tritium and begins the fusion stage. The flux of neutrons from the fusion reactions causes the \ce{^{238}U} tamper to undergo fission. At this stage the device breaks apart and a detonation is complete \cite{Defense1998}.

@@

\subsection{Pre-Detonation Nuclear Forensics}

Following the interception of SNM or weapon components, careful analysis of the composition, material structure, and relative sophistication of the physics package will allow forensic investigators to estimate the age of the device, the techniques which were utilized in order to create the physics package, and the most probable country of origin \cite{Glaser2008}. In the U.S., a number of organizations would be involved in these assessments. The National Technical Nuclear Forensics Center (NTNFC) is responsible for ensuring the nation's nuclear forensics capability.  The NTNFC is supported by the Department of Homeland Security (DHS), Department of Justice (DOJ), Federal Bureau of Investigation (FBI), Department of Defense (DoD), Department of Energy (DOE), Department of State (DOS), and the Office of the Director of National Intelligence (ODNI) \cite{DepartmentOfHomelandSecurit}.

The age of the physics package is determined from the composition. Because SNM is, itself, radioactive, a small amount of mass is converted to heat and radiates off. It is possible to approximate the change in mass by estimating the age of the original physics package based on the apparent design of the weapon; this change in mass correlates to the age of the device since the physics package was created \cite{Inn2013}. See

\subsubsection{?????? This section hasn't been created yet  ???????}

\enquote{Methods of Active Interrogation,}

\subsubsection{??????  Add ref to this Tech Appendix, once it's done   ??????}

in \autoref{} for a description of the technical means of estimating the composition of SNM. The country of origin for Uranium-based weapons may be narrowed down based on the initial enrichment of the material \cite{Defense1998}. The facility of origin may be determined in Plutonium-based designs based on the ratio of isotopes present, as shown in \autoref{fig:pu_signatures}.

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.3]{./figures/pu_signatures.png}
   \caption{The expected and measured ratio of isotopes of Plutonium, listed by facility of origin \cite{B412922A}.}
     \label{fig:pu_signatures}
\end{figure}

The manufacturing techniques could be determined from micro-analytical techniques which measure the oxidation state and crystalline form of the special nuclear material; however, the results of such studies are often inconclusive and may require up to a few weeks for a complete analysis \cite{Drell1995}. Additional details on the nature and implementation of pre-detonation forensics are listed in reference \cite{Doyle2011}.
